TUDataset: A collection of benchmark datasets for learning with graphs

### 2020-06-07 main.tex
MC.

			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}  &   $52.3$ \scriptsize $\pm 0.7 \pm 6.7 $       & $72.6$ \scriptsize $\pm  0.6 \pm 4.1$ &  $50.3$ \scriptsize $\pm 0.8 \pm  3.8 $ & $84.5$ \scriptsize $\pm 0.3 \pm 1.7$ & $72.8$ \scriptsize $\pm 0.8 \pm  3.9 $ & $73.9$ \scriptsize $\pm 0.6 \pm 3.2$  \\
			%				& \text{2-LWL} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
			%				& \text{2-LWL$^+$} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
			& \text{WLOA} & $58.4$ \scriptsize $\pm 2.0 \pm 7.4$       &  $73.2$ \scriptsize $\pm 0.8 \pm 3.8$ & $49.4$ \scriptsize $\pm 0.3 \pm 3.6 $ & $85.4$ \scriptsize $\pm  0.2 \pm 1.4$ & $73.2$ \scriptsize $\pm 0.6 \pm 3.5$ & $88.4$ \scriptsize $\pm 0.4 \pm 2.1 $   \\
			& \text{GR}            &    $30.1$ \scriptsize $\pm 0.8 \pm 6.0$       & $59.0$ \scriptsize $\pm 0.9 \pm 5.7$ & $39.6$ \scriptsize $\pm 0.5 \pm 3.6  $ & $66.2$ \scriptsize $\pm 0.2\pm 2.2$ & $71.4$ \scriptsize $\pm 0.6\pm 4.4 $ & $60.0$ \scriptsize $\pm 0.2 \pm  2.7$   \\
			& \text{SP}            & $40.5$  \scriptsize $\pm 1.6 \pm 6.2$       & $58.7$ \scriptsize $\pm 0.9 \pm 4.6 $ & $39.5$ \scriptsize $\pm 0.9 \pm 4.2$ & $74.5$ \scriptsize $\pm 0.4\pm 2.2 $  &$75.9$ \scriptsize $\pm 0.6 \pm 4.0$ & $84.6$ \scriptsize $\pm0.2\pm 0.4 $  \\
			\cmidrule{2-8}	
			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \textsc{Gin-$\varepsilon$}   &   \scriptsize $\pm \pm $       & $72.4$ \scriptsize $\pm 0.6\pm 4.0 $ &  $49.7$ \scriptsize $\pm 0.2 \pm  3.9$ & $79.0$ \scriptsize $\pm  0.5 \pm 1.9 $ &  $71.3$ \scriptsize $\pm 0.4 \pm 4.0$ & $90.0$ \scriptsize $\pm 0.6 \pm 1.7 $   \\
			& \textsc{Gin-$\varepsilon$-JK} &     \scriptsize $\pm \pm $       & $73.4$ \scriptsize $\pm 0.6\pm 4.4$ & $50.6$ \scriptsize $\pm 0.5 \pm 4.2 $ & $79.1$ \scriptsize $\pm  0.2 \pm 1.5 $ & $72.4$ \scriptsize $\pm 0.6 \pm 1.7 $ & $90.6$ \scriptsize $\pm 0.2 \pm  2.2$   \\
			\bottomrule
	\end{tabular}}
\end{table*}		
\begin{table*}[t]\centering		
	\caption{Classification accuracies in percent and standard deviations,  \textsc{OOT}--- Computation did not finish within one day, \textsc{OOM}--- Out of memory.}
	\label{t2l}	
	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{.9}
		\begin{tabular}{@{}c <{\enspace}@{}lccccc@{}}	\toprule
			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{5}{c}{\textbf{Dataset}}\\\cmidrule{3-7}
			& & {\textsc{Mcf-7}}         &  {\textsc{Molt-4}}      & {\textsc{Yeast}}           & {\textsc{github\_star.}}       & {\textsc{reddit\_threads}}      \\	\toprule
			\multirow{3}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}    & 
			$94.5$ \scriptsize $<0.1 \pm 0.4$  &$94.6$ \scriptsize $\pm 0.1  \pm 0.3$ & $89.2$ \scriptsize $\pm 0.1 \pm 0.4$ &  $63.9$ \scriptsize $\pm 0.1\pm 1.3$ &$77.0$ \scriptsize $<0.1 \pm 0.3$  \\

@@

\xhdr{Graph kernels.} As kernel baselines we used the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphket}~\cite{She+2009}, \new{Weisfeiler-Lehman Optimal Assigment} \textsc{WL-OA}~\cite{Kri+2016} included in the \textsc{TUDataset} package. The $C$-parameter was selected from $\{10^{-3}, 10^{-2}, \dotsc, 10^{2},$ $10^{3}\}$ from the validation set. For the larger datasets, we computed sparse feature vectors for each graph and used the linear $C$-SVM implementation of \text{Liblinear}~\cite{Fan+2008}. The number of iterations of the \textsc{$1$-WL}, \textsc{WL-OA}, and the  $\delta$-$2$-LWL$^+$ were selected from $\{0,\dotsc,5\}$.\footnote{As already shown in~\cite{She+2011}, choosing the number of iterations too large will lead to overfitting.}

@@

\subsection{Results and discussion}
See~\cref{t2l}.

@@

For \textsc{Zinc}, we used the given train, validation split, test split, and report the MAE over the test set. For the \textsc{Alchemy} dataset, we uniformly and at random sampled 80\% of the graphs for training, and 10\% for validation and testing, respectively. Moreover, following~\cite{Che+2020,Gil+2017}, we normalized the targets of the training split to zero mean and unit variance. We used a single model to predict all targets. Following~\cite{Kli+2020}, we report mean standardized MAE and mean standardized logMAE. We repeated each experiment five times (with different random splits in case of \textsc{Alchemy}) and report average scores and standard deviations. All neural experiments were conducted on a workstation with four Nvidia Tesla V100 GPU cards with 32GB of GPU memory running Oracle Linux Server 7.7.

>>>>

			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}  &   $52.3$ \scriptsize $\pm 0.7 \pm 6.7 $       & $72.6$ \scriptsize $\pm  0.6 \pm 4.1$ &  $50.3$ \scriptsize $\pm 0.8 \pm  3.8 $ & $84.5$ \scriptsize $\pm 0.3 \pm 1.7$ & $72.8$ \scriptsize $\pm 0.8 \pm  3.9 $ & $73.9$ \scriptsize $\pm 0.6 \pm 3.2$  \\
			%				& \text{2-LWL} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
			%				& \text{2-LWL$^+$} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
			& \text{WLOA} & $58.4$ \scriptsize $\pm 2.0 \pm 7.4$       &  $73.2$ \scriptsize $\pm 0.8 \pm 3.8$ & $49.4$ \scriptsize $\pm 0.3 \pm 3.6 $ & $85.4$ \scriptsize $\pm  0.2 \pm 1.4$ & $73.2$ \scriptsize $\pm 0.6 \pm 3.5$ & $88.4$ \scriptsize $\pm 0.4 \pm 2.1 $   \\
			& \text{GR}            &    $30.1$ \scriptsize $\pm 0.8 \pm 6.0$       & $59.0$ \scriptsize $\pm 0.9 \pm 5.7$ & $39.6$ \scriptsize $\pm 0.5 \pm 3.6  $ & $66.2$ \scriptsize $\pm 0.2\pm 2.2$ & $71.4$ \scriptsize $\pm 0.6\pm 4.4 $ & $60.0$ \scriptsize $\pm 0.2 \pm  2.7$   \\
			& \text{SP}            & $40.5$  \scriptsize $\pm 1.6 \pm 6.2$       & $58.7$ \scriptsize $\pm 0.9 \pm 4.6 $ & $39.5$ \scriptsize $\pm 0.9 \pm 4.2$ & $74.5$ \scriptsize $\pm 0.4\pm 2.2 $  &$75.9$ \scriptsize $\pm 0.6 \pm 4.0$ & $84.6$ \scriptsize $\pm0.2\pm 0.4 $  \\
			\cmidrule{2-8}	
			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \textsc{Gin-$\varepsilon$}   &   \scriptsize $\pm \pm $       & $72.4$ \scriptsize $\pm 0.6\pm 4.0 $ &  $49.7$ \scriptsize $\pm 0.2 \pm  3.9$ & $79.0$ \scriptsize $\pm  0.5 \pm 1.9 $ &  $71.3$ \scriptsize $\pm 0.4 \pm 4.0$ & $90.0$ \scriptsize $\pm 0.6 \pm 1.7 $   \\
			& \textsc{Gin-$\varepsilon$-JK} &     \scriptsize $\pm \pm $       & $73.4$ \scriptsize $\pm 0.6\pm 4.4$ & $50.6$ \scriptsize $\pm 0.5 \pm 4.2 $ & $79.1$ \scriptsize $\pm  0.2 \pm 1.5 $ & $72.4$ \scriptsize $\pm 0.6 \pm 1.7 $ & $90.6$ \scriptsize $\pm 0.2 \pm  2.2$   \\
			\bottomrule
	\end{tabular}}
\end{table*}		
\begin{table*}[t]\centering		
	\caption{Classification accuracies in percent and standard deviations,  \textsc{OOT}--- Computation did not finish within one day, \textsc{OOM}--- Out of memory.}
	\label{t2ll}	
	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{.9}
		\begin{tabular}{@{}c <{\enspace}@{}lccccc@{}}	\toprule
			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{5}{c}{\textbf{Dataset}}\\\cmidrule{3-7}
			& & {\textsc{Mcf-7}}         &  {\textsc{Molt-4}}      & {\textsc{Yeast}}           & {\textsc{github\_star.}}       & {\textsc{reddit\_threads}}      \\	\toprule
			\multirow{3}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}    & 
			$94.5$ \scriptsize $<0.1 \pm 0.4$  &$94.6$ \scriptsize $\pm 0.1  \pm 0.3$ & $89.2$ \scriptsize $\pm 0.1 \pm 0.4$ &  $63.9$ \scriptsize $\pm 0.1\pm 1.3$ &$77.0$ \scriptsize $<0.1 \pm 0.3$  \\

@@

\xhdr{Graph kernels.} As kernel baselines we used the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphket}~\cite{She+2009}, \new{Weisfeiler-Lehman Optimal Assigment} \textsc{WL-OA}~\cite{Kri+2016} included in the \textsc{TUDataset} package. The $C$-parameter was selected from $\{10^{-3}, 10^{-2}, \dotsc, 10^{2},$ $10^{3}\}$ from the validation set. For the larger datasets, we computed sparse feature vectors for each graph and used the linear $C$-SVM implementation of \text{Liblinear}~\cite{Fan+2008}. The number of iterations of the \textsc{$1$-WL} and \textsc{WL-OA} were selected from $\{0,\dotsc,5\}$.\footnote{As already shown in~\cite{She+2011}, choosing the number of iterations too large will lead to overfitting.}

@@

\subsection{Results and discussion}
See~\cref{t2l,t2ll,neural_short_tt}. On the small-scale datasets, see \cref{t2l}, the \textsc{WLOA} performs best overall, i.e., only on the \textsc{IMDB-Binary} and the \textsc{Reddit-Binary} dataset it is beating by the the $1$-\textsc{WL} or the neural baselines. However, it does not scale midscale datasets, \cref{t2l}, as it relies on Gram matrix computation. Here, the $1$-WL performs, excluding \textsc{github\_stargazers}, where the neural baseline perform best overall.

@@

For \textsc{Zinc}, we used the given train, validation split, test split, and report the MAE over the test set. For the \textsc{Alchemy} and \textsc{QM9} datasets, we uniformly and at random sampled 80\% of the graphs for training, and 10\% for validation and testing, respectively. Moreover, following~\cite{Che+2020,Gil+2017}, we normalized the targets of the training split to zero mean and unit variance. We used a single model to predict all targets. Following~\cite{Kli+2020}, we report mean standardized MAE and mean standardized logMAE. We repeated each experiment five times (with different random splits in case of \textsc{Alchemy}) and report average scores and standard deviations.  Moreover, we use learning rate decay of $0.5$ with a patience parameter of $5$ with starting learning rate of $0.001$ and a minimum of $10^{-6}$.

For the \textsc{QM9} dataset, we additionally used the \textsc{MPNN}~\cite{Gil+2017} architecture as a baseline, closely following the setup of~\cite{Gil+2017}. For the (\textsc{Gine-$\varepsilon$}  and the \textsc{MPNN} architecture, following~\citeauthor{Gil+2017}~\cite{Gil+2017}, we used a complete graph, computed pairwise $\ell_2$ distances based on the 3D-coordinates, and concatenated them to the edge features. We note here that our intent is not the beat state-of-the-art, physical knowledge-incorporating architectures, e.g., \textsf{DimeNet}~\cite{Kli+2020} or \textsf{Cormorant}~\cite{And+2019}, but to solely provide baseline scores.

All neural experiments were conducted on a workstation with four Nvidia Tesla V100 GPU cards with 32GB of GPU memory running Oracle Linux Server 7.7.
